\chapter{Acknowledgment}

I want to first thank my thesis advisor Professor
Rochelle Leibowitz for pushing me to find significant results.
Without her help,
I would not be able to come up with most of the important
ideas in this thesis.

Then, I want to thank my parents for being supportive
during my toughest days of writing this thesis.
My father said to me,
``Being truly innovative is always a struggle,
but not everyone is great enough
to ever experience this kind of hardship.''
I want to share this thought with you --- future thesis students.
Hope it will help you get pass
the hardest days of your researches.

I want to thank all friends and professors who
reviewed this thesis and provided useful feedbacks.
These professors are three members of my thesis committee:
Professor Rochelle Leibowitz,
Professor William Bloch,
and Professor John Gildea,
as well as friends, including
my dearest girlfriend and best friend, Shi Shen;
two of my most valuable and talented friends,
Xinyi Liu and Xinru Liu;
my only friend who is good with grammar, Yuchen Wang
(if there is any grammatical error here,
it is her fault).

I want to thank Professor William Bloch
for his Real Analysis course,
which drew me into mathematics.
I also want to thank Professor Martin Gagné
for his Theory of Computation course,
which introduced me to the field of theoretical computer science.
Without taking these courses,
I would not pursue my Ph.D degree in Type Thoery.

Finally I want to thank again all my dear friends
including Shi Shen, Xinyi Liu, Xinru Liu, Fiona Xu, Weiqi Feng,
Yuchen Wang, and many others
for these fun and memorable four years of college.
Most importantly,
I want to express my gratitude to all professors
who I had classes with.
They not only taught me with knowledge,
but also prepared me to face future challenges.
